---
title: "Group Project"
author: "Nicholas Kwak"
date: "12/25/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Visualization/project Design
# Import dataset

```{r}
main.data = read.csv("BigML_Dataset_5f50a62c2fb31c516d000176.csv")
```

# Import tidyverse and ggplot2
```{r}
library(tidyverse)
library(ggplot2)
```

# Keep relevent data, remove everything else

```{r}
# Select also changed order of columns.  Ratings and popularity are less relevent for questions we asked.
movie.data = main.data %>% select(movie,certificate,duration,
                                  genre, gross, awards_wins, awards_nominations, 
                                  Oscar_nominated, rate, metascore, popularity)
```

```{r}
# Save modifications to csv file.
write.csv(movie.data, "movie.data.csv")

```

# Boxplot relating the number of nominations with total number of awards the film got (includes awards unrelated to Oscars).  Removed outliers 
```{r}
boxplot(awards_wins~Oscar_nominated, data = movie.data,
        xlab = "Number of Oscar Nominations",
        ylab = "Awards Won",
        outline = FALSE)
```

Using ggplot2
```{r}
ggplot(data = movie.data, aes(x=Oscar_nominated, y=awards_wins)) +
  geom_boxplot(aes(group = Oscar_nominated), fill = "gold", outlier.shape = NA) +
  labs(title = "Boxplot relating Oscar Nominations to Awards Won", 
       x = "Number of Oscar Nominations", y="Total Number of Awards Won")
```

# Removed blank entries for certificate using filter.  
```{r}
rating = filter(movie.data,certificate != "")
boxplot(awards_wins~certificate, data = rating,
        xlab = "Age Demographic",
        ylab = "Awards Won",
        outline = FALSE)
```


Using ggplot2
```{r}
ggplot(data = rating, aes(x=certificate, y=awards_wins)) +
  geom_boxplot(aes(group = certificate, fill = certificate), outlier.shape = NA) +
  labs(title = "Boxplot relating Age Rating and Awards Won", 
       x = "Age Rating", y="Total Number of Awards Won",
       fill = "Legend")

```

# Scatterplot with both merged (won't really help I think)
```{r}
ggplot(data = rating, aes(x=Oscar_nominated, y=awards_wins, color = certificate), outlier.shape = NA) + geom_point() + 
  labs(title = "Boxplot relating Age Rating and Awards Won", 
       x = "Age Rating", y="Total Number of Awards Won",
       fill = "Legend")

```

#Graph using profit
```{r}

```